---
title: DATA 606 Final Project
author: Wei Zhou
output: 
  html_document:
    theme: cerulean
    toc: true
    toc_float: true
---

### Data Preparation

```{r setup, echo=TRUE, results='hide', warning=FALSE, message=FALSE}
# load data
library(dplyr)
library(nycflights13)
library(ggplot2)

head(flights,10)
names(flights)
```


### Research question 

**You should phrase your research question in a way that matches up with the scope of inference your dataset allows for.**

Is there any relationship between origin airport and and probability of delay? 

** Why do you care? Why should others care?**
Working as a consultant, one will spend a good amount of time in Airport. If the research indicates there is a relationship between departure airport and probability of delay, one can consider the airport factor to avoid potential delay. 

##Data

### Cases 

**What are the cases, and how many are there?**

```{r}
nrow(flights)
summary(flights$year)
```

Cases are each flights information departure from EWR,JFK,LGA in 2013. 

The are 336776 cases.


### Data collection 

**Describe the method of data collection.**

Data is clollected by the 'dplyr' library. It contains all airline on-time data for all flights departing NYC in 2013. 

**If you collected the data, state self-collected. If not, provide a citation/link.**

https://github.com/hadley/nycflights13


### Type of study 

**What type of study is this (observational/experiment)?**

Observational study

###Variables

**Dependent Variable: What is the response variable? Is it quantitative or qualitative?**

The response variable is airline delay or not
```{r}
flights=flights%>%
  mutate(dep_delay_bool=ifelse(dep_delay>=0,'ontime','delay'))
class(flights$dep_delay_bool)
```

**Independent Variable: You should have two independent variables, one quantitative and one qualitative.**
```{r}
class(flights$origin)
```


### Scope of inference
**generalizability: Identify the population of interest, and whether the findings from this analysis can be generalized to that population, or, if not, a subsection of that population. Explain why or why not. Also discuss any potential sources of bias that might prevent generalizability.**


Population of interest: Flights departure from NYC airport. 
The finding from this analys can be generalized to the population.

**causality: Can these data be used to establish causal links between the variables of interest? Explain why or why not.**
These data cannot be used to establish causal links between the origin airport and departure delay. Chi-square test can only indicate correlationship between two categorical relationship. 


### Exploratory data analysis:

#### Relevant summary statistics 
**Provide summary statistics for each the variables. Also include appropriate visualizations related to your research question (e.g. scatter plot, boxplots, etc). This step requires the use of R, hence a code chunk is provided below. Insert more code chunks as needed.**

#### Delay proportion
55% of the NYC flights are delayed,only 44% were on time.
```{r}
table(flights$dep_delay_bool)
prop.table(table(flights$dep_delay_bool))

```
**Barchart showing the proportion of departure delay and on time.**
```{r}
ggplot(flights,aes(1 ,fill =dep_delay_bool )) + 
    geom_bar(position = "fill")+
    coord_flip()
```

#### number of flights by each departure airport
**EWR had the most flights comparing to JFK and LGA**
```{r}
table(flights$origin)
prop.table(table(flights$origin))
```

#### Contingency table : Airport v.s. Delay
**According to the historical data, EWR had the least delay rate (50.4%), by comparing with JFK (55.9%) and LGA (62.1%)**
```{r}
table(flights$origin, flights$dep_delay_bool)
prop.table(table(flights$origin, flights$dep_delay_bool),1)
```
```{r}
ggplot(flights,aes(origin ,fill =dep_delay_bool )) + 
    geom_bar(position = "fill")+
    ggtitle("Airport Delay Proportion")
```
###Delay rate by time
**It is also interesting to see the delay rate changed by time**
#### By Year
```{r}
flights%>%
  na.omit()%>%
  mutate(delay_rate = ifelse(dep_delay_bool=='delay',1,0))%>%
  group_by(month)%>%
  summarize(delay = round(mean(delay_rate),2))%>%
  ggplot(aes(month,delay))+
  geom_line(color='blue')+
  geom_text(aes(label=delay),hjust=0, vjust=0)
  
```

###Inference

#### Check Conditions
1. The sampling method is simple random sampling.

2. The variables under study are each categorical.

3. When sample data are displayed in a contingency table, the  frequency count for each cell of the table are all more than 5.

#### Chi-square test

To test the relationship between Origin Airport and Delay using Pearson's Chi-square test, we need to set null and alternative hypothesis: 

Null Hypothesis: The Origin Airport and Departure Delay Senario are independent with each other
Alternative Hypothesis: The Origin Airport and Departure Delay Senario are not independent with each other
```{r}
chi_sq_tbl=table(flights$origin, flights$dep_delay_bool)
chisq.test(chi_sq_tbl)
```
From the above result, we can see that p-value is less than the significance level (0.05). Therefore, we can reject the null hypothesis and conclude that the two variables (Origin Airport & Departure Delay) are not independent.

###Conclusion
Given the result of Chi-square test, we can conclude that the origin airport and delayed departure are not independent with each other. Thus, if you are on a time sensitive business trip, it is important to take Origin Airport as a factor to avoid potential departure delay. In the future research, it is also interesting to explore how time (Year,Month,hour) and weather affect departure delay. 




