---
title: DATA 606 Data Project Proposal
author: Wei Zhou
---

### Data Preparation

```{r setup, echo=TRUE, results='hide', warning=FALSE, message=FALSE}
# load data
library(dplyr)
library(nycflights13)
library(ggplot2)

head(flights,10)
names(flights)
```


### Research question 

**You should phrase your research question in a way that matches up with the scope of inference your dataset allows for.**

Is there any relationship between origin airport and and probability of delay? 


### Cases 

**What are the cases, and how many are there?**

```{r}
nrow(flights)
summary(flights$year)
```

Cases are each flights information departure from EWR,JFK,LGA in 2013. 

The are 336776 cases.

### Data collection 

**Describe the method of data collection.**

Data is clollected by the 'dplyr' library. It contains all airline on-time data for all flights departing NYC in 2013. 


### Type of study 

**What type of study is this (observational/experiment)?**

Observational study


### Data Source 

**If you collected the data, state self-collected. If not, provide a citation/link.**

https://github.com/hadley/nycflights13


### Dependent Variable

**What is the response variable? Is it quantitative or qualitative?**

The response variable is airline delay or not
```{r}
flights=flights%>%
  mutate(dep_delay_bool=ifelse(dep_delay>=0,'ontime','delay'))

class(flights$dep_delay_bool)
```

### Independent Variable

**You should have two independent variables, one quantitative and one qualitative.**
```{r}
class(flights$origin)
```

### Relevant summary statistics 
**Provide summary statistics for each the variables. Also include appropriate visualizations related to your research question (e.g. scatter plot, boxplots, etc). This step requires the use of R, hence a code chunk is provided below. Insert more code chunks as needed.**

###### Delay proportion
```{r}
table(flights$dep_delay_bool)
prop.table(table(flights$dep_delay_bool))
```

###### number of flights by each departure airport
```{r}
table(flights$origin)
prop.table(table(flights$origin))

```

###### Contingency table : Airport v.s. Delay
```{r}
table(flights$origin, flights$dep_delay_bool)
prop.table(table(flights$origin, flights$dep_delay_bool),1)
```




