---
title: "Data606_hw7_weizhou"
author: "Wei Zhou"
date: "4/13/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 7.24 Nutrition at Starbucks, Part I.

#####a. Describe the relationship between number of calories and amount of carbohydrates (in grams) that Starbucks food menu items contain.

It seems there is a weak positive relationship between the number of calories and amount of carbohydrates . 

#####b. In this scenario, what are the explanatory and response variables?
Calories is explanatory and carbs is response. 

#####c. why might we want to fit a regression line to these data?
Customers would like to kow how many Calories on average are coming from carbs.

#####d. Do these data meet the conditions required for fitting a least squares line?
No. The residuals are not constant as residuals increase as the calories increase.


## 7.26 Body measurements, Part III.

#####a.Write the equation of the regression line for predicting height.
```{r}
avg_shoulder = 107.20 
sd_shoulder = 10.37 
avg_height = 171.14 
sd_height = 9.41 
cor = 0.67 

b1 <- (sd_height/sd_shoulder) * cor
b0 <- avg_height - b1 * avg_shoulder
b1
b0
```
Equation: y= `r b1`X + `r b0`

##### b. Interpret the slope and the intercept in this context.
Slope = `r b1` means every 1 cm increase in should girth, the height increase by `r b1` cm on average

Intercept = `r b0` means if a person has 0 cm in shoulder girth, the person should be 105.9561 cm tall on average. 

##### c. Calculate R2 of the regression line for predicting height from shoulder girth, and interpret it in the context of the application.
R2=0.4489. 44.89% of the variation is accounter for should girth. 

##### d. A randomly selected student from your class has a shoulder girth of 100 cm. Predict the height of this student using the model.

```{r}
pred = b1*100+b0
pred
```

##### e. The student from part (d) is 160 cm tall. Calculate the residual, and explain what this residual means.
```{r}
residual = pred - 160 
residual
```
Residual is `r residual`. It means there is a `r residual` cm difference between the prediction and the actual observation. 


##7.30 Cats, Part I. 

#####a. Write out the linear model.

```{r}
b0 = -0.357
b1 = 4.034 
```
y = `r b1`X - `r -b0` 

#####b.  Interpret the intercept.
The intercept here means the off-set between the body mass and heart mass. 

#####c. Interpret the slope
The slope means the heart weight increase 4.034 g over 1 kg increase in body weight. 

#####d. Interpret R2.
64.66% of the heart weight variation is explained by the cat's body mass. 

#####e. Calculate the correlation coefficient. 
```{r}
r2 = 0.6466 
r = sqrt(r2)
r
```


##7.40 Rate my professor.

##### a. Given that the average standardized beauty score is -0.0883 and average teaching evaluation score is 3.9983, calculate the slope. Alternatively, the slope may be computed using just the information provided in the model summary table.

```{r}
b0 <- 4.010
x <- -.0883
y <- 3.9983
b1 = (y-b0)/x
b1
```

##### b.Do these data provide convincing evidence that the slope of the relationship between teaching evaluation and beauty is positive? Explain your reasoning.
The p-value=0.0000 mean the model is statistically significant. The slope seems large enough






