---
title: "Data606_hw5_weizhou"
author: "Wei Zhou"
date: "3/23/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library('DATA606')
library('knitr')
```



## Exercise 5.6 Working backwards

#### Part II. A 90% confidence interval for a population mean is (65, 77). The population distribution is approximately normal and the population standard deviation is unknown. This confidence interval is based on a simple random sample of 25 observations. Calculate the sample mean, the margin of error, and the sample standard deviation.

```{r}
lower = 65
upper = 77 
n = 25 
mean = (lower+upper) / 2 
margin_error = (upper - lower) / 2 
t = qt(0.95,25-1) 
sd = (margin_error / t) * 5
mean
margin_error
sd
```
mean = 71   
margin_error = 6    
sd = 17.53481 


## Exercise 5.14 SAT scores. 

#### (a) Raina wants to use a 90% confidence interval. How large a sample should she collect?
```{r}
ME = 25
SD = 250
z = qnorm(0.95)
n = ((SD*z)/ME)^2
n
```
The sample size should at least have 271 students. 


#### (b) Luke wants to use a 99% confidence interval. Without calculating the actual sample size, determine whether his sample should be larger or smaller than Raina’s, and explain your reasoning.

Luke's sample size should be larger than Raina's sample size. Z(ci=0.95) < Z(ci=0.99). The sample size is positively affected by the Z score. Thus Luke's sample size should be larger. 

#### (c) Calculate the minimum required sample size for Luke.

```{r}
ME = 25
SD = 250
z = 2.58
n = ((SD*z)/ME)^2
n
```
The minimun requirement sample size for Luke is 666 students. 

##5.20 High School and Beyond, Part I

#### (a) Is there a clear difference in the average reading and writing scores?

It seems no clear difference in the average reading and writing scores. 


#### (b) Are the reading and writing scores of each student independent of each other?

Reading and writing scires if each student are not independent. 

#### (c) Create hypotheses appropriate for the following research question: is there an evident difference in the average scores of students in the reading and writing exam?

`H0` There is no evident difference in the average scores of students in the reading and writing exam at the significance level of 0.05

`HA` There is evident difference in the average scores of students in the reading and writing exam at the significance level of 0.05

#### (d) Check the conditions required to complete this test.
1. Observations is randomly selected from the population. 
2. Distribution normal and not strongly skewwed   
3. Sample is large than 30 observations    
4. Homogeneous, or equal variance exists when the standard deviations of samples are approximately equal. 

#### (e) Observed difference in scores is x¯read−write=-0.545,sd of diff = 8.887. Do these data provide convincing evidence of a difference between the average scores on the two exams?

```{r}
mean = -0.545 
sd = 8.887
n =200 
se = sd / sqrt(n)
t = (mean - 0 ) / se 
p = pt(t,n-1)
p
```
Since the p-value 0.1934 is greater than  0.05 , we fail to reject the null hypothesis there is no evident difference in the aerage scores of students in the reading and writing exam at the significance level of 0.05 


#### (f) What type of error might we have made? Explain what the error means in the context of the application.
We may already made type 2 error and concluded that there is no a difference in the average score of reading and writing by mistake. 

#### (g) Based on the results of this hypothesis test, would you expect a confidence interval for the average difference between the reading and writing scores to include 0? Explain your reasoning.
Yes, it should include 0. It is because we conclude that there is no difference in the average score of reading and writing.


## 5.32 Fuel efficiency of manual and automatic cars, Part I.

##### Each year the US Environmental Protection Agency (EPA) releases fuel economy data on cars manufactured in that year. Below are summary statistics on fuel e“ciency (in miles/gallon) from random samples of cars with manual and automatic transmissions manufactured in 2012. Do these data provide strong evidence of a di???erence between the average fuel e”ciency of cars with manual and automatic transmissions in terms of their average city mileage? Assume that conditions for inference are satisfied. 

`H0` There is no significant difference in average fuel efficiency of cars with manual and automatic transmission in terms of their average city milage.     
`HA` There is significant difference in average fuel efficiency of cars with manual and automatic transmission in terms of their average city milage. 
```{r}
n= 26 
sd_a = 3.58 
sd_m = 4.51 
mean_a = 16.12 
mean_m = 19.85

se_a = sd_a / sqrt(n)
se_m = sd_m / sqrt(n)

se = sqrt(se_a^2 + se_m^2)
t = ((mean_a - mean_m)-0) / se
p = pt(t,n-1)
p_2 <- 2*p 
p_2

```
The p-value is 0.002884 which is less than 0.05. Therefore I can reject the null hypothesis and conclude that there is significant difference in average fuel efficiency of cars with manual and automatic transmission in terms of their average city milage. 


## 5.48 Work hours and education. 

#### (a) Write hypotheses for evaluating whether the average number of hours worked varies across the five groups.
`H0` The difference of all averages are equal    
`HA` There is one average that is not equal to the other ones. 


#### (b) Check conditions and describe any assumptions you must make to proceed with the test.
1. Observations are independent within and across groups.   
2. Distributions of each group are normal and not strongly skewwed.
3. Homogeneous, or equal variance exists when the standard deviations of samples are approximately equal. 
4. The sample size is larger than 30. 

#### (c) Below is part of the output associated with this test. Fill in the empty cells.


#### (d) 
```{r}
n= 1172 
n_group = 5
mean_sq_degree = 501.54
sum_sq_residual = 267382

####df######
df_degree = n_group-1 
df_residual = n-n_group
df_total = n-1

####sq####
mean_sq_residual = sum_sq_residual / df_residual
sum_sq_degree = df_degree *mean_sq_degree 
sum_sq_total = sum_sq_residual + sum_sq_degree
###f### 
f = mean_sq_degree / mean_sq_residual

row_name = c('degree','residual','total')
df =  c(df_degree,df_residual,df_total)
mean_sq = c(mean_sq_degree,mean_sq_residual,NA)
sum_sq = c(sum_sq_degree,sum_sq_residual,sum_sq_total)
f_ls = c(f,NA,NA)

results = data.frame(row_name,df,sum_sq,mean_sq,f_ls)
results
```

#### (d) What is the conclusion of the test?
Since the p-value is 0.0681932, which is larger than 0.05, we failed to reject the null hypothesis that there is no difference among the average of each group. 



